Modelling the Lymphatic Metastatic Progression Pathways of OPSCC from Multi-Institutional Datasets

### 2023-08-29 src/tex/ms.tex
[showyourwork] overleaf sync

{\it Level VII:} The two models' predictions w.r.t. the prevalence of involvement patterns that include \gls{lnl} VII are not compared in a dedicated figure, as this level is only connected to the primary tumor in both graphs.

\begin{figure}
    \script{comp_VII_prevs.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/comp_VII_prevs.png}
        \caption{TODO: Write caption}
        \label{fig:VII_prevs}
    \end{centering}
\end{figure}

>>>>

{\it Level VII:} The two models' predictions w.r.t. the prevalence of involvement patterns that include \gls{lnl} VII are compared in \cref{fig:VII_prevs}. Here, the base and winning graph yield almost the same predictions, as no new edge connects from or to \gls{lnl} VII in the latter model. Notably, the prevalence of early T-category level VII involvement is slightly overestimated, while for late T-category, the fit is very good.

\begin{figure}
    \script{comp_VII_prevs.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/comp_VII_prevs.png}
        \caption{Predictions for the prevalence of \gls{lnl} VII involvement based on the base graph (hatched) and the winning graph (blue histogram) plotted agains the beta posterior over the prevalence in the data (solid line).}
        \label{fig:VII_prevs}
    \end{centering}
\end{figure}
